---
title: "Reproducible Analyses"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- Using manuscript + supplement from https://drive.google.com/drive/u/0/folders/1_lBKpwcRFFIUcJZq8XENDovHmMNC8m5I

- Using analyses from https://drive.google.com/drive/u/0/folders/1V00hNRQofmBxloVls-Vxy1t30henrzGw

- Using pre-registration from https://docs.google.com/document/d/1nCfUY9tJLBk41vE_BU56S10rrBoRdVaMwDFo1DMZy8M/edit?tab=t.0#heading=h.fwbi14d4b65g

## Libraries

```{r}
library(rio)
library(dplyr)
library(psych)
library(dplyr)
library(tidyr)
library(stringr)
library(lavaan)
library(broom)
library(sirt)
library(sf)
library(rnaturalearth)
library(viridis)
library(patchwork)
library(beepr)
library(readr)
library(misty)
library(ggplot2)
library(lme4)
library(parameters)
library(performance)
library(apaTables)

pct <- function(x) round(100 * x, 1)

largest_group <- function(vec) {
  tab <- prop.table(table(vec))
  top <- names(which.max(tab))
  p <- pct(max(tab, na.rm = TRUE))
  paste0(top, " (", p, "%)")
}

RUN_MODEL <- TRUE # change me to rerun models
```

## Session Info

```{r}
sessionInfo()
```

## Robustness Analysis Notes

* This analysis includes only participants with complete data for analyses *after* the model building. 
* Recoding sections were included to ensure the same structure for analyses. 

# Data

```{r import-data}
# load data
dt <- import("../data/processed_data/dhf_data_final.csv.zip")
```

## Sample Summary

```{r clean-variable-names}
#L: variable names changed to match the new data
factorized_var_numbers<-
  c(which(names(dt)=="gender"),
    which(names(dt)=="Migration"),
    which(names(dt)=="location_childhood"),
    which(names(dt)=="location_current"),
    which(names(dt)=="ethnicity"),
    which(names(dt)=="religion"),
    which(names(dt)=="education"),
    which(names(dt)=="student"),
    which(names(dt)=="income"),
    which(names(dt)=="Country"),
    which(names(dt)=="country_res_full"),
    which(names(dt)=="Sample"),
    which(names(dt)=="datasource"))

numeric_var_numbers<-
  c(which(names(dt)=="Age"))

# refactor gender, age, education, state, race, migration 
dt[,factorized_var_numbers] <- lapply(dt[,factorized_var_numbers], as.factor)
dt[,numeric_var_numbers] <- as.numeric(dt[,numeric_var_numbers])
```

```{r reciprocity-scoring}
# recode variables to numeric
dt <- dt %>%
  mutate_at(vars(Reciprocity_1:Reciprocity_6), ~dplyr::case_when(
    . == "Does not apply to me at all\r\n1\r\n" ~ 1,
    . == "1" ~ 1,
    . == "2" ~ 2,
    . == "3" ~ 3,
    . == "4" ~ 4,
    . == "5" ~ 5,
    . == "6" ~ 6,
    . == "7" ~ 6,
    . == "Applies to me perfectly\r\n7\r\n" ~ 7,
    TRUE ~ NA_integer_
  ))

# examine data
Recprocity_first_num <- which(names(dt)=="Reciprocity_1")
Recprocity_last_num <- which(names(dt)=="Reciprocity_6")

# calculate positive and negative reciprocity  
dt$Positive_Reciprocity <- rowMeans(dt[c("Reciprocity_1","Reciprocity_2","Reciprocity_3")], na.rm=TRUE)
dt$Negative_Reciprocity <- rowMeans(dt[c("Reciprocity_4","Reciprocity_5","Reciprocity_6")], na.rm=TRUE)
```

* exclude participants who are too young 

```{r demographic-clean}
# exclude participants who are <18
dt1 <- subset(dt, Age >=18|is.na(Age))
```

* remove people who were not bord and raised in the country 

```{r migration-data}
# NAs are cases where question was not shown, so include
dt2 <- subset(dt1, Migration==1|Migration==3|is.na(Migration)) #n=35901 
```

* remove due to attention checks

```{r attention-checks}
# exclude participants who failed 2 or 3 attention checks, except for ALLS countries where attention checks were not shown
dt2$attention1 <- ifelse(dt2$attention_1==2|dt2$datasource == "ALLS", 1, 0)
dt2$attention2 <- ifelse(dt2$attention_2==5|dt2$datasource == "ALLS", 1, 0)
dt2$attention3 <- ifelse(dt2$attention_3==3|dt2$datasource == "ALLS", 1, 0)
dt2$attention <- rowSums(dt2[c("attention1", "attention2", "attention3")], na.rm=T)
dt3 <- subset(dt2, attention>=2) 
```

* remove due to too small sample 

```{r country-exclude}
# exclude countries with <50 participants and where country is missing
# table(dt3$country_res_full, useNA = "ifany")
dt3$country_res_full <- as.factor(dt3$country_res_full)

dt4 <- dt3 %>%
  group_by(country_res_full) %>%
  filter(!is.na(country_res_full) & n() >= 50) %>%
  ungroup() %>%
  mutate(country_res_full = droplevels(country_res_full))

#all -99 and -999 in the dataset are now assigned as missing 
dt4[dt4 == -99] <- NA
dt4[dt4 == -999] <- NA
```

## Create Indices

```{r create-indices}
# Ensure Schwartz values are merged (if not already done in the reliability check stage)
print("Ensuring Schwartz values are merged...")
for(i in 1:21) {
  col_name <- paste0("values_", i)
  col_n <- paste0("values_n_", i)
  col_m <- paste0("values_m_", i)  
  col_f <- paste0("values_f_", i)
  
  if(all(c(col_n, col_m, col_f) %in% names(dt4))) {
    dt4 <- dt4 %>%
      mutate(!!col_name := coalesce(!!sym(col_n), !!sym(col_m), !!sym(col_f)))
  }
}

print("CREATING SCALE INDICES")
print(paste(rep("=", 50), collapse = ""))

# Function to calculate mean with at least 50% valid responses
calculate_scale_mean <- function(data, vars, min_valid_prop = 0.5) {
  # Check which variables exist
  available_vars <- vars[vars %in% names(data)]
  
  if(length(available_vars) == 0) {
    return(rep(NA, nrow(data)))
  }
  
  # Calculate means requiring at least 50% valid responses
  scale_data <- data[, available_vars, drop = FALSE]
  n_items <- ncol(scale_data)
  min_valid <- ceiling(n_items * min_valid_prop)
  
  # Calculate row means with minimum valid responses
  row_means <- rowMeans(scale_data, na.rm = TRUE)
  valid_count <- rowSums(!is.na(scale_data))
  
  # Set to NA if insufficient valid responses
  row_means[valid_count < min_valid] <- NA
  
  return(row_means)
}

# Create all scale indices
print("1. Creating reciprocity indices...")

# 1. RECIPROCITY
dt4 <- dt4 %>%
  mutate(
    Positive_Reciprocity = calculate_scale_mean(., c("Reciprocity_1", "Reciprocity_2", "Reciprocity_3")),
    Negative_Reciprocity = calculate_scale_mean(., c("Reciprocity_4", "Reciprocity_5", "Reciprocity_6"))
  )

print("2. Creating violence attitude indices...")

# 2. VIOLENCE ATTITUDES
dt4 <- dt4 %>%
  mutate(
    Penal_Code_Violence = calculate_scale_mean(., c("violence_1", "violence_2", "violence_3")),
    War_Acceptance = calculate_scale_mean(., c("violence_4", "violence_5", "violence_6")),
    Corporal_Punishment = calculate_scale_mean(., c("violence_7", "violence_8", "violence_9")),
    Intimate_Violence = calculate_scale_mean(., c("violence_10", "violence_11", "violence_12")),
    Total_Violence = calculate_scale_mean(., paste0("violence_", 1:12))
  )

print("3. Creating face concern indices...")

# 3. FACE CONCERNS
dt4 <- dt4 %>%
  mutate(
    Other_Face_Concern = calculate_scale_mean(., c("conflict_face_2", "conflict_face_3", "conflict_face_4", 
                                                   "conflict_face_5", "conflict_face_6", "conflict_face_7")),
    Self_Face_Concern = calculate_scale_mean(., c("conflict_face_8", "conflict_face_9", "conflict_face_10", "conflict_face_11"))
  )

print("4. Creating reactions to insult indices (excluding 3rd scenario)...")

# 4. REACTIONS TO PROVOCATION (excluding 3rd scenario items due to problematic alpha)
dt4 <- dt4 %>%
  mutate(
    Withdrawal = calculate_scale_mean(., c("insult1_1", "insult2_1")),
    Retaliation = calculate_scale_mean(., c("insult1_2", "insult2_2")),
    Humor = calculate_scale_mean(., c("insult1_3", "insult2_3"))
  )

print("5. Creating Schwartz higher-order values indices...")

# 5. SCHWARTZ HIGHER-ORDER VALUES
dt4 <- dt4 %>%
  mutate(
    Self_Transcendence = calculate_scale_mean(., paste0("values_", c(3, 8, 19, 12, 18))),
    Self_Enhancement = calculate_scale_mean(., paste0("values_", c(4, 13, 2, 17))),
    Openness_to_Change = calculate_scale_mean(., paste0("values_", c(1, 11, 6, 15, 10, 21))),
    Conservation = calculate_scale_mean(., paste0("values_", c(5, 14, 7, 16, 9, 20)))
  )

print("6. Creating moral foundations indices...")

# 6. MORAL FOUNDATIONS
dt4 <- dt4 %>%
  mutate(
    MFQ_Care = calculate_scale_mean(., paste0("MFQ_", c(1, 7, 13, 19, 25, 31))),
    MFQ_Equality = calculate_scale_mean(., paste0("MFQ_", c(2, 8, 14, 20, 26, 32))),
    MFQ_Proportionality = calculate_scale_mean(., paste0("MFQ_", c(3, 9, 15, 21, 27, 33))),
    MFQ_Loyalty = calculate_scale_mean(., paste0("MFQ_", c(4, 10, 16, 22, 28, 34))),
    MFQ_Authority = calculate_scale_mean(., paste0("MFQ_", c(5, 11, 17, 23, 29, 35))),
    MFQ_Purity = calculate_scale_mean(., paste0("MFQ_", c(6, 12, 18, 24, 30, 36)))
  )

print("7. Creating religiosity indices...")

# 7. INTRINSIC RELIGIOSITY (raw scores)
dt4 <- dt4 %>%
  mutate(
    Intrinsic_Religiosity = calculate_scale_mean(., c("relig_intrinsic_1", "relig_intrinsic_2", "relig_intrinsic_3"))
  )

# 8. COMPOSITE RELIGIOSITY (standardized scores)
print("8. Creating composite religiosity index (standardized scores)...")

# Check if religiosity variables exist
religiosity_vars <- c("relig_attendance", "relig_private", "relig_intrinsic_1", "relig_intrinsic_2", "relig_intrinsic_3")
available_relig_vars <- religiosity_vars[religiosity_vars %in% names(dt4)]

if(length(available_relig_vars) > 0) {
  # Standardize each religiosity variable
  dt4_standardized <- dt4
  for(var in available_relig_vars) {
    dt4_standardized[[paste0(var, "_z")]] <- scale(dt4[[var]])[,1]
  }
  
  # Calculate composite score from standardized variables
  standardized_vars <- paste0(available_relig_vars, "_z")
  dt4$Composite_Religiosity <- calculate_scale_mean(dt4_standardized, standardized_vars)
  
  cat("Composite religiosity created using:", paste(available_relig_vars, collapse = ", "), "\n")
} else {
  dt4$Composite_Religiosity <- NA
  cat("Warning: Religiosity variables not found. Composite religiosity set to NA.\n")
}

print("9. Creating subjective well-being index...")

# 9. SUBJECTIVE WELL-BEING
dt4 <- dt4 %>%
  mutate(
    Subjective_Wellbeing = calculate_scale_mean(., c("swbls_1", "swbls_2", "swbls_3", "swbls_4", "swbls_5"))
  )

# List all created indices
created_indices <- c(
  "Positive_Reciprocity", "Negative_Reciprocity",
  "Penal_Code_Violence", "War_Acceptance", "Corporal_Punishment", "Intimate_Violence", "Total_Violence",
  "Other_Face_Concern", "Self_Face_Concern",
  "Withdrawal", "Retaliation", "Humor",
  "Self_Transcendence", "Self_Enhancement", "Openness_to_Change", "Conservation",
  "MFQ_Care", "MFQ_Equality", "MFQ_Proportionality", "MFQ_Loyalty", "MFQ_Authority", "MFQ_Purity",
  "Intrinsic_Religiosity", "Composite_Religiosity", "Subjective_Wellbeing"
)

print("\nCreated indices:")
print(created_indices)
```

## Include Clustering Variable for Later

```{r optim-clustering}
dt4$cluster <- recode_factor(dt4$country_res_full, 
                             "Argentina" = "Latin America",
                             "Brazil" = "Latin America",
                             "Chile" = "Latin America",
                             "Mexico" = "Latin America",
                             "Armenia" = "Eastern Europe",
                             "Bosnia-Herzegovina" = "Eastern Europe",
                             "Bulgaria" = "Eastern Europe",
                             "Croatia" = "Eastern Europe",
                             "Czech Republic" = "Eastern Europe",
                             "Georgia" = "Eastern Europe",
                             "Greece" = "Eastern Europe",
                             "Hungary" = "Eastern Europe",
                             "Kosovo" = "Eastern Europe",
                             "North Macedonia" = "Eastern Europe",
                             "Poland" = "Eastern Europe",
                             "Russia" = "Eastern Europe",
                             "Serbia" = "Eastern Europe",
                             "Slovakia" = "Eastern Europe",
                             "Kazakhstan" = "Eastern Europe",
                             "Ukraine" = "Eastern Europe",
                             "Australia" = "Anglo-Saxon",
                             "Canada" = "Anglo-Saxon",
                             "New Zealand" = "Anglo-Saxon",
                             "Ireland" = "Anglo-Saxon",
                             "United Kingdom" = "Anglo-Saxon",
                             "United States" = "Anglo-Saxon",
                             "Austria" = "Germanic",
                             "Germany" = "Germanic",
                             "Switzerland" = "Germanic",
                             "The Netherlands" = "Germanic",
                             "Bangladesh" = "South-East Asia",
                             "India" = "South-East Asia",
                             "Indonesia" = "South-East Asia",
                             "Iran" = "South-East Asia",
                             "Malaysia" = "South-East Asia",
                             "Pakistan" = "South-East Asia",
                             "Philippines" = "South-East Asia",
                             "Thailand" = "South-East Asia",
                             "Cameroon" = "Africa",
                             "Ethiopia" = "Africa",
                             "Kenya" = "Africa",
                             "Namibia" = "Africa",
                             "Nigeria" = "Africa",
                             "South Africa" = "Africa",
                             "Ghana" = "Africa",
                             "China" = "Confucian",
                             "Japan" = "Confucian",
                             "Singapore" = "Confucian",
                             "Hong Kong" = "Confucian",
                             "Taiwan" = "Confucian",
                             "Vietnam" = "Confucian",
                             "France" = "Latin Europe",
                             "Israel" = "Latin Europe",
                             "Italy" = "Latin Europe",
                             "Portugal" = "Latin Europe",
                             "Romania" = "Latin Europe",
                             "Spain" = "Latin Europe",
                             "Kuwait" = "Middle East",
                             "Morocco" = "Middle East",
                             "Saudi Arabia" = "Middle East",
                             "Lebanon" = "Middle East",
                             "Turkey" = "Middle East",
                             "Uzbekistan" = "Middle East",
                             "United Arab Emirates" = "Middle East")

dt4[dt4 == -99] <- NA
```

## Missing Data

* for this robustness test run only on people who have these variables 

```{r missing-data-calc}
# variables they need 
vars_needed <- c(
  # dictator
  "Dictator.comp1.1_dich", "Dictator.comp2.1_dich", "Dictator.comp1.2_dich", 
  "Dictator.comp2.2_dich", "Dictator_decision", 
  # ultimatum
  "Ultimatum.comp.1.1_dich", "Ultimatum.comp.2.1_dich", "Ultimatum.comp.1.2_dich", 
  "Ultimatum.comp.2.2_dich", "Ultimatum.Receiver_1", "Ultimatum.Receiver_2", 
  "Ultimatum.Receiver_3", "Ultimatum.Receiver_4", "Ultimatum.Receiver_5", 
  "Ultimatum.Receiver_6", "Ultimatum.Receiver_7", "Ultimatum.Receiver_8", 
  "Ultimatum.Receiver_9", "Ultimatum.Receiver_10", "Ultimatum.Receiver_11", 
  "Ultimatum.Proposer_1", "Ultimatum.Proposer_2", 
  "Ultimatum.Proposer_3", "Ultimatum.Proposer_4", "Ultimatum.Proposer_5", 
  "Ultimatum.Proposer_6", "Ultimatum.Proposer_7", "Ultimatum.Proposer_8", 
  "Ultimatum.Proposer_9", "Ultimatum.Proposer_10", "Ultimatum.Proposer_11",
  # dhf scores
  "dhf_endors_1", "dhf_endors_2", "dhf_endors_3", "dhf_endors_4", "dhf_endors_5", 
  "dhf_endors_6", "dhf_endors_7", "dhf_endors_8", "dhf_endors_9", "dhf_endors_10", 
  "dhf_endors_11", "dhf_endors_12", "dhf_endors_13", "dhf_endors_14", "dhf_endors_15", 
  "dhf_endors_16", "dhf_endors_17", "dhf_endors_18", "dhf_endors_19", "dhf_endors_20", 
  "dhf_endors_21", "dhf_endors_22", "dhf_endors_23", "dhf_endors_24", "dhf_endors_25", 
  "dhf_endors_26", "dhf_endors_27", "dhf_endors_28", "dhf_endors_29", "dhf_endors_30", 
  "dhf_norm_1", "dhf_norm_2", "dhf_norm_3", "dhf_norm_4", "dhf_norm_5", 
  "dhf_norm_6", "dhf_norm_7", "dhf_norm_8", "dhf_norm_9", "dhf_norm_10", 
  "dhf_norm_11", "dhf_norm_12", "dhf_norm_13", "dhf_norm_14", "dhf_norm_15", 
  "dhf_norm_16", "dhf_norm_17", "dhf_norm_18", "dhf_norm_19", "dhf_norm_20", 
  "dhf_norm_21", "dhf_norm_22", "dhf_norm_23", "dhf_norm_24", "dhf_norm_25", 
  "dhf_norm_26", "dhf_norm_27", "dhf_norm_28", "dhf_norm_29", "dhf_norm_30", 
  # other face
  "conflict_face_2", "conflict_face_3", "conflict_face_4", "conflict_face_5", 
  "conflict_face_6", "conflict_face_7", "conflict_face_8", "conflict_face_9", 
  "conflict_face_10", "Other_Face_Concern", "Self_Face_Concern",
  # other cultural variables
  "Openness_to_Change", "Conservation", "Self_Transcendence", "Self_Enhancement",
  # reciprocity
  "Reciprocity_1","Reciprocity_2","Reciprocity_3", "Positive_Reciprocity", 
  "Reciprocity_4","Reciprocity_5","Reciprocity_6", "Negative_Reciprocity",
  # violence
  "violence_1", "violence_2", "violence_3", "violence_4", "violence_5", 
  "violence_6", "violence_7", "violence_8", "violence_9", "violence_10", 
  "violence_11", "violence_12", "Total_Violence",
  # withdrawal, retaliation, humor
  "insult1_1", "insult2_1", "Withdrawal", 
  "insult1_2", "insult2_2", "Retaliation",
  "insult1_3", "insult2_3", "Humor"
  )

country_vars_needed <- c("wb_pop_density_1961", "ms_pathogen_9items", 
                         "icb_crisis_participations", 
                         "icb_avg_violence_level",
                         "wb_gdp_pcap_usd_1960", "fiw_F_2013", 
                         "fiw_C_2013", "fiw_Total_2013", 
                         "wb_gdp_pcap_usd_most_recent", "gii_value_2021", 
                         "wb_gini_2020", "fiw_Total_2023", "hdi_value_2021", 
                         "tl_tightness", "mk_individualism_collectivism", 
                         "mk_flexibility_monumentalism", "rm_relational_mobility",
                         "country_res_full", "ResponseId", "cluster")

dt4 <- dt4 %>% 
  filter(if_all(all_of(vars_needed), ~ !is.na(.))) %>% 
  select(all_of(c(vars_needed, country_vars_needed)))

nrow(dt4)
```

## Prosocial Behavior 

### Dictator Game

```{r}
# dictator game
dt4$dictator_cpass <- ifelse((dt4$Dictator.comp1.1_dich=="Correct"|dt4$Dictator.comp2.1_dich=="Correct")&(dt4$Dictator.comp1.2_dich=="Correct"|dt4$Dictator.comp2.2_dich=="Correct"),1,0)
table(dt4$dictator_cpass, useNA = "ifany")
dt5 <- subset(dt4, dictator_cpass==1) 
# use dt5 for all tests that involve the Dictator Game 

# dictator = universal prosociality for our experiment
dt5$prosocial <- as.numeric(dt5$Dictator_decision)
# examine the data 
describe(dt5$prosocial) #Mean=4.77, SD=1.75, median=5
```

### Ultimatum Game

```{r}
# ultimatum game
dt4$ultimatum_cpass <- ifelse((dt4$Ultimatum.comp.1.1_dich=="Correct"|dt4$Ultimatum.comp.2.1_dich=="Correct")&(dt4$Ultimatum.comp.1.2_dich=="Correct"|dt4$Ultimatum.comp.2.2_dich=="Correct"),1,0)
dt6 <- subset(dt4, ultimatum_cpass==1) #N=20626

##use dt6 for all tests that involve the Ultimatum Game##

# ultimatum_receiver = negative reciprocity
# select those rows 
receiver <- dt6 %>% 
  select(ResponseId, `Ultimatum.Receiver_1`:`Ultimatum.Receiver_11`)

# convert to long format for scoring
receiver_long <- receiver %>%
  pivot_longer(!ResponseId, names_to = "proposed", values_to = "decision")

# score the ultimatum receiver game - adapted for the coding (1=accept, 2=reject)
receiver_long$change <- ifelse(receiver_long$decision == 1 & 
                                 (((receiver_long$decision != dplyr::lag(receiver_long$decision))==TRUE)|
                                    (receiver_long$proposed=="Ultimatum.Receiver_1")),1,0)

receiver_long$proposed <- str_remove(receiver_long$proposed, "Ultimatum.Receiver_")
receiver_long$UG_negrec <- ifelse(receiver_long$change==1, receiver_long$proposed, 0)

neg_rec_df <- subset(receiver_long, receiver_long$UG_negrec!=0)
neg_rec_df$dupl <- ifelse(duplicated(neg_rec_df$ResponseId)==TRUE, 1, 0)
neg_rec_df <- subset(neg_rec_df, neg_rec_df$dupl==0)
neg_rec_df <- neg_rec_df %>% 
  select(ResponseId, UG_negrec)

# Merge with dt6
dt6 <- merge(dt6, neg_rec_df, by="ResponseId")
dt6$UG_negrec <- as.numeric(dt6$UG_negrec)

# examine data
# 100*table(dt6$`Ultimatum.Receiver_1`) %>% prop.table() 
100*table(dt6$`Ultimatum.Receiver_2`) %>% prop.table() 
# 100*table(dt6$`Ultimatum.Receiver_3`) %>% prop.table() 
# 100*table(dt6$`Ultimatum.Receiver_4`) %>% prop.table() 
# 100*table(dt6$`Ultimatum.Receiver_5`) %>% prop.table() 

# ultimatum_proposer = positive reciprocity
proposer <- dt6 %>% 
  select(ResponseId, `Ultimatum.Proposer_1`:`Ultimatum.Proposer_11`)

# pivot longer to score the data 
proposer_long <- proposer %>%
  pivot_longer(!ResponseId, names_to = "proposed", values_to = "decision")

proposer_long$proposed <- str_remove(proposer_long$proposed, "Ultimatum.Proposer_")
proposer_long[, c("proposed", "decision")] <- lapply(proposer_long[, c("proposed", "decision")], as.numeric)
proposer_long$proposed <- proposer_long$proposed - 1

# cor.test(proposer_long$proposed, proposer_long$decision) 
# r between proposal to and from = .605***  
describe(proposer_long$decision) 
# m=4.89 (4.89/11*100=44.5%)

proposer_long$pr <- ifelse(proposer_long$decision >= proposer_long$proposed, 1, 0)
pos_rec_df <- aggregate(proposer_long$pr, by=list(proposer_long$ResponseId), FUN=sum)
pos_rec_df$UG_posrec <- (pos_rec_df$x/11)*100
pos_rec_df$ResponseId <- pos_rec_df$Group.1
pos_rec_df <- pos_rec_df %>% 
  select(ResponseId, UG_posrec)

# create merged dataset
dt6 <- merge(dt6, pos_rec_df, by="ResponseId")
```

### Correlations between Reciprocity

```{r}
# examine correlations (adapted variable names)
cor.test(dt6$Positive_Reciprocity, dt6$UG_posrec) 
cor.test(dt6$Positive_Reciprocity, dt6$UG_negrec) 

cor.test(dt6$Negative_Reciprocity, dt6$UG_negrec) 
cor.test(dt6$Negative_Reciprocity, dt6$UG_posrec)
```

## Main Study

### Main study: DHF scores across the world 

```{r calculate-means-endorse}
# calculate participant means for DHF endorsement
dt4 <- dt4  %>% 
  mutate(
    D_self_end = rowMeans(select(.,dhf_endors_1:dhf_endors_5), na.rm=T),
    D_other_end = rowMeans(select(.,dhf_endors_6:dhf_endors_10),na.rm=T),
    H_self_end = rowMeans(select(.,dhf_endors_11:dhf_endors_15),na.rm=T),
    H_other_end = rowMeans(select(.,dhf_endors_16:dhf_endors_20),na.rm=T),
    F_self_end = rowMeans(select(.,dhf_endors_21:dhf_endors_25),na.rm=T),
    F_other_end = rowMeans(select(.,dhf_endors_26:dhf_endors_30),na.rm=T),
    D_end = rowMeans(select(.,dhf_endors_1:dhf_endors_10),na.rm=T),
    H_end = rowMeans(select(.,dhf_endors_11:dhf_endors_20),na.rm=T),
    F_end = rowMeans(select(.,dhf_endors_21:dhf_endors_30),na.rm=T)
  )
# endorsement corrected for response style (within-participant centering)
dt4 <- dt4  %>% 
  mutate(dhf_endors_mean = rowMeans(select(.,dhf_endors_1:dhf_endors_30), na.rm=T))

dt4 <- dt4  %>% 
  mutate(
    D_self_endc = D_self_end - dhf_endors_mean,
    D_other_endc = D_other_end - dhf_endors_mean,
    H_self_endc = H_self_end - dhf_endors_mean,
    H_other_endc = H_other_end - dhf_endors_mean,
    F_self_endc = F_self_end - dhf_endors_mean,
    F_other_endc = F_other_end - dhf_endors_mean,
    D_endc = D_end - dhf_endors_mean,
    H_endc = H_end - dhf_endors_mean,
    F_endc = F_end - dhf_endors_mean,
  )

# calculate country means for endorsement
country_endors <- dt4 %>%
  group_by(country_res_full) %>%
  summarize(
    across(
      c(D_self_end, D_other_end, H_self_end, H_other_end, F_self_end, F_other_end, D_end, H_end, F_end, D_self_endc, D_other_endc, H_self_endc, H_other_endc, F_self_endc, F_other_endc, D_endc, H_endc, F_endc),
      ~mean(., na.rm = TRUE),
      .names = "{.col}_mean_country"
    )
  )

dt4 <- dt4 %>%
  left_join(country_endors, by = "country_res_full")
```

```{r calculate-means-norms}
# calculate participant means for DHF norms 
dt4 <- dt4  %>% 
  mutate(
    D_self_norm = rowMeans(select(.,dhf_norm_1:dhf_norm_5), na.rm=T),
    D_other_norm = rowMeans(select(.,dhf_norm_6:dhf_norm_10),na.rm=T),
    H_self_norm = rowMeans(select(.,dhf_norm_11:dhf_norm_15),na.rm=T),
    H_other_norm = rowMeans(select(.,dhf_norm_16:dhf_norm_20),na.rm=T),
    F_self_norm = rowMeans(select(.,dhf_norm_21:dhf_norm_25),na.rm=T),
    F_other_norm = rowMeans(select(.,dhf_norm_26:dhf_norm_30),na.rm=T),
    D_norm = rowMeans(select(.,dhf_norm_1:dhf_norm_10),na.rm=T),
    H_norm = rowMeans(select(.,dhf_norm_11:dhf_norm_20),na.rm=T),
    F_norm = rowMeans(select(.,dhf_norm_21:dhf_norm_30),na.rm=T)
  )

# endorsement corrected for response style (within-participant centering)
dt4 <- dt4  %>% 
  mutate(dhf_norm_mean = rowMeans(select(.,dhf_norm_1:dhf_norm_30), na.rm=T))

dt4 <- dt4  %>% 
  mutate(
    D_self_normc = D_self_norm - dhf_norm_mean,
    D_other_normc = D_other_norm - dhf_norm_mean,
    H_self_normc = H_self_norm - dhf_norm_mean,
    H_other_normc = H_other_norm - dhf_norm_mean,
    F_self_normc = F_self_norm - dhf_norm_mean,
    F_other_normc = F_other_norm - dhf_norm_mean,
    D_normc = D_norm - dhf_norm_mean,
    H_normc = H_norm - dhf_norm_mean,
    F_normc = F_norm - dhf_norm_mean,
  )

# calculate country means for endorsement
country_norm <- dt4 %>%
  group_by(country_res_full) %>%
  summarize(
    across(
      c(D_self_norm, D_other_norm, H_self_norm, H_other_norm, F_self_norm, F_other_norm, D_norm, H_norm, F_norm, D_self_normc, D_other_normc, H_self_normc, H_other_normc, F_self_normc, F_other_normc, D_normc, H_normc, F_normc),
      ~mean(., na.rm = TRUE),
      .names = "{.col}_mean_country"
    )
  )

dt4 <- dt4 %>%
  left_join(country_norm, by = "country_res_full")
```

DHF endorsement and norms scores (centered) across world regions 

```{r print-means-dhf}
dt4 %>% 
  select(
    D_self_end, D_other_end, H_self_end, H_other_end, F_self_end, F_other_end, D_end, H_end, F_end, 
    D_self_endc:F_endc, D_self_normc:F_normc, cluster) %>% 
  group_by(cluster) %>% 
  summarize(
    across(
      c(D_self_end, D_other_end, H_self_end, H_other_end, F_self_end, F_other_end, D_end, H_end, F_end, D_self_endc, D_other_endc, H_self_endc, H_other_endc, F_self_endc, F_other_endc, D_endc, H_endc, F_endc),
      ~mean(., na.rm = TRUE),
      .names = "{.col}_mean_region"
    ),
    across(
      c(D_self_end, D_other_end, H_self_end, H_other_end, F_self_end, F_other_end, D_end, H_end, F_end, D_self_endc, D_other_endc, H_self_endc, H_other_endc, F_self_endc, F_other_endc, D_endc, H_endc, F_endc),
      ~sd(., na.rm = TRUE),
      .names = "{.col}_sd_region"
    )
  )
```

DHF endorsement and norms scores (centered) across countries

```{r print-means-dhf-country}
country_endors

country_norm
```

#### Visualizations

Cleveland dot plot of Honor/Face/Dignity norms by country (non-centered)

```{r h2-visualization-dotplot-noncentered}
# 1) Reshape to long format (one row per country × dimension)
df_long <- country_norm %>%
  select(
    country_res_full,
    Honor   = H_norm_mean_country,
    Face    = F_norm_mean_country,
    Dignity = D_norm_mean_country
  ) %>%
  pivot_longer(Honor:Dignity, names_to = "Dimension", values_to = "Score")

# 2) Choose how to order countries on the y-axis
#    Option A: by overall mean across the 3 dimensions (lowest → highest)
country_order <- df_long %>%
  group_by(country_res_full) %>%
  summarise(mean_score = mean(Score, na.rm = TRUE), .groups = "drop") %>%
  arrange(mean_score) %>%
  pull(country_res_full)

#    (Alternative)
#    # Option B: by Honor only
#    country_order <- df_long %>% filter(Dimension == "Honor") %>%
#      arrange(Score) %>% pull(country_res_full)
#
#    # Option C: alphabetical
#    country_order <- sort(unique(df_long$country_res_full))

# 3) Apply the order so ggplot respects it
df_long$country_res_full <- factor(df_long$country_res_full, levels = country_order)

# 4) Precompute per-country ranges (min→max across the three dimensions)
ranges <- df_long %>%
  group_by(country_res_full) %>%
  summarise(
    xmin = min(Score, na.rm = TRUE),
    xmax = max(Score, na.rm = TRUE),
    .groups = "drop"
  )

# 5) Plot
p <- ggplot() +
  # grey range bars (min→max per country)
  geom_segment(
    data = ranges,
    aes(x = xmin, xend = xmax, y = country_res_full, yend = country_res_full),
    color = "grey70",
    linewidth = 0.4
  ) +
  # colored points for the three dimensions
  geom_point(
    data = df_long,
    aes(x = Score, y = country_res_full, color = Dimension),
    size = 2.5, alpha = 0.8,
    # Use small vertical jitter if overlapping points are an issue; keep width at 0 for x
    position = position_jitter(height = 0, width = 0)
    # If you prefer perfectly aligned dots, use: position = position_identity()
  ) +
  # Color palette: Dark2 is colorblind-friendly; remove legend title
  scale_color_brewer(palette = "Dark2", name = NULL) +
  labs(x = "Societal mean (1-7)", y = NULL, title = NULL) +
  # Minimal theme + enforce true white background
  theme_minimal(base_size = 12) +
  theme(
    panel.background    = element_rect(fill = "white", color = NA),
    plot.background     = element_rect(fill = "white", color = NA),
    panel.grid.major.y  = element_blank(),     # cleaner y axis
    axis.text.y         = element_text(size = 10),
    legend.position     = "top"
  )

p

# 6) Save
#    Adjust height if you have many countries (more rows → more height).
ggsave(
  filename = "figures_robust/DHF_Norms_dotplot_noncentered.png",
  plot = p,
  width = 9, height = 14, dpi = 600
)

# Vector version for journals (crisp text/lines):
ggsave(
  filename = "figures_robust/DHF_Norms_dotplot_noncentered.pdf",
  plot = p,
  width = 9, height = 14
)
```

Cleveland dot plot of Honor/Face/Dignity norms by country (non-centered & centered)

```{r h2-visualization-dotplot}
# 1) Long data for NON-centered
df_nc <- country_norm %>%
  select(
    country_res_full,
    Honor   = H_norm_mean_country,
    Face    = F_norm_mean_country,
    Dignity = D_norm_mean_country
  ) %>%
  pivot_longer(Honor:Dignity, names_to = "Dimension", values_to = "Score") %>%
  mutate(Centering = "Non-centered")

# 2) Long data for CENTERED (same dimension names)
df_c <- country_norm %>%
  select(
    country_res_full,
    Honor   = H_normc_mean_country,
    Face    = F_normc_mean_country,
    Dignity = D_normc_mean_country
  ) %>%
  pivot_longer(Honor:Dignity, names_to = "Dimension", values_to = "Score") %>%
  mutate(Centering = "Centered")

# 3) Combine + set factor orders
df_both <- bind_rows(df_nc, df_c) %>%
  mutate(
    Dimension = factor(Dimension, levels = c("Honor","Face","Dignity")),
    Centering = factor(Centering, levels = c("Non-centered","Centered"))
  )

# 4) Fix a single country order (so both facets share the same y-axis)
#    Here: order by the NON-centered average across the 3 dimensions (intuitive baseline)
country_order <- df_nc %>%
  group_by(country_res_full) %>%
  summarise(mean_score = mean(Score, na.rm = TRUE), .groups = "drop") %>%
  arrange(mean_score) %>%
  pull(country_res_full)

df_both$country_res_full <- factor(df_both$country_res_full, levels = country_order)

# 5) (Optional) draw per-country range segments across the 3 dimensions *within each facet*
ranges <- df_both %>%
  group_by(Centering, country_res_full) %>%
  summarise(
    xmin = min(Score, na.rm = TRUE),
    xmax = max(Score, na.rm = TRUE),
    .groups = "drop"
  )

# 6) Plot: one panel per Centering; dots colored by Dimension
set.seed(123)  # reproducible jitter

p <- ggplot() +
  # grey connector showing spread across the three dimensions for each country in each facet
  geom_segment(
    data = ranges,
    aes(x = xmin, xend = xmax, y = country_res_full, yend = country_res_full),
    color = "grey70", linewidth = 0.4
  ) +
  # three dots per country (Honor/Face/Dignity)
  geom_point(
    data = df_both,
    aes(x = Score, y = country_res_full, color = Dimension),
    size = 2.5, alpha = 0.75,
    position = position_jitter(height = 0, width = 0)  # small vertical separation
  ) +
  facet_wrap(~ Centering, nrow = 1, scales = "free_x") +  # free_x lets centered vs non-centered have their own scales
  scale_color_brewer(palette = "Dark2", name = NULL) +
  labs(x = "Societal mean (1-7)", y = NULL, title = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.background   = element_rect(fill = "white", color = NA),
    plot.background    = element_rect(fill = "white", color = NA),
    panel.grid.major.y = element_blank(),
    axis.text.y        = element_text(size = 10),
    legend.position    = "top"
  )

p

# 7) Save (increase height for many countries)
ggsave("figures_robust/DHF_Norms_dotplot.png", p,
       width = 18, height = 14, dpi = 600)
ggsave("figures_robust/DHF_Norms_dotplot.pdf", p,
       width = 18, height = 14)
```

World map of Honor/Face/Dignity norms (non-centered scores)

```{r h2-visualization-worldmap-noncentered}
# --- 1) World polygons (drop Antarctica for cleaner view) ---
# Uses Natural Earth country names for joining. Currently in geographic (WGS84) CRS.
# If you want Robinson, add: world <- st_transform(world, "+proj=robin") after this block.
world <- ne_countries(scale = "medium", returnclass = "sf") |>
  select(name, geometry) |>
  filter(name != "Antarctica")

# --- 2) Rename and recode to EXACT Natural Earth names ---
# Harmonize your dataset's country labels to match Natural Earth.
# Add more entries to recode() as mismatches arise.
country_data <- country_norm |>
  transmute(
    name    = country_res_full,
    Honor   = H_norm_mean_country,
    Face    = F_norm_mean_country,
    Dignity = D_norm_mean_country
  ) |>
  mutate(
    name = dplyr::recode(
      name,
      "Bosnia-Herzegovina" = "Bosnia and Herzegovina",
      "Czech Republic"     = "Czechia",
      "The Netherlands"    = "Netherlands",
      "United States"      = "United States of America"
    )
  )

# --- 3) Join to polygons ---
# Left join keeps all polygons; countries without data will map as NA (filled by na.value).
world_join <- world |> left_join(country_data, by = "name")

# (Optional) quickly see if any still unmatched
# Use this to catch remaining naming issues and extend recode() above.
# anti_join(country_data, st_drop_geometry(world), by = "name") |> distinct(name)

# --- 4) Long form + consistent limits across facets (so colors are comparable) ---
# Non-centered scores: keep a single limit across all three to make colors comparable row-wise.
world_long <- world_join |>
  select(geometry, Honor, Face, Dignity) |>
  pivot_longer(c(Honor, Face, Dignity),
               names_to = "Dimension", values_to = "Score") |>
  mutate(Dimension = factor(Dimension, levels = c("Honor","Face","Dignity")))

# Set limits explicitly for reproducibility; alternatively use range(world_long$Score, na.rm=TRUE).
lims <- c(3,5.5) # range(world_long$Score, na.rm = TRUE)

# --- 5) Plot: titles centered, thin white borders, compact legend ---
# Apply the same basic theme to all six maps; legends will later be collected per row.
common_theme <- theme(
  plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
  legend.position = "bottom",
  legend.title = element_text(size = 10),
  legend.text  = element_text(size = 9)
)

# Non-centered maps (viridis option "C")
p_honor <- ggplot(filter(world_long, Dimension == "Honor")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Honor norms") +
  theme_void() +
  common_theme

p_face <- ggplot(filter(world_long, Dimension == "Face")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Face norms") +
  theme_void() +
  common_theme

p_dignity <- ggplot(filter(world_long, Dimension == "Dignity")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Dignity norms") +
  theme_void() +
  common_theme

# ---- build plot for non-centered scores only ----
p <- (p_honor | p_face | p_dignity) +
  plot_layout(guides = "collect") &
  theme(
    legend.position  = "bottom"
  )
p

# Export plot
ggsave("figures_robust/DHF_Norms_worldmap_noncentered.png", p,
       width = 18, height = 4, dpi = 600)
ggsave("figures_robust/DHF_Norms_worldmap_noncentered.pdf", p,
       width = 18, height = 4)
```

World map of Honor/Face/Dignity norms

```{r h2-visualization-worldmap}
# --- 1) World polygons (drop Antarctica for cleaner view) ---
# Uses Natural Earth country names for joining. Currently in geographic (WGS84) CRS.
# If you want Robinson, add: world <- st_transform(world, "+proj=robin") after this block.
world <- ne_countries(scale = "medium", returnclass = "sf") |>
  select(name, geometry) |>
  filter(name != "Antarctica")

# --- 2) Rename and recode to EXACT Natural Earth names ---
# Harmonize your dataset's country labels to match Natural Earth.
# Add more entries to recode() as mismatches arise.
country_data <- country_norm |>
  transmute(
    name    = country_res_full,
    Honor   = H_norm_mean_country,
    Face    = F_norm_mean_country,
    Dignity = D_norm_mean_country,
    HonorC   = H_normc_mean_country,
    FaceC    = F_normc_mean_country,
    DignityC = D_normc_mean_country,
  ) |>
  mutate(
    name = dplyr::recode(
      name,
      "Bosnia-Herzegovina" = "Bosnia and Herzegovina",
      "Czech Republic"     = "Czechia",
      "The Netherlands"    = "Netherlands",
      "United States"      = "United States of America"
    )
  )

# --- 3) Join to polygons ---
# Left join keeps all polygons; countries without data will map as NA (filled by na.value).
world_join <- world |> left_join(country_data, by = "name")

# (Optional) quickly see if any still unmatched
# Use this to catch remaining naming issues and extend recode() above.
# anti_join(country_data, st_drop_geometry(world), by = "name") |> distinct(name)

# --- 4) Long form + consistent limits across facets (so colors are comparable) ---
# Non-centered scores: keep a single limit across all three to make colors comparable row-wise.
world_long <- world_join |>
  select(geometry, Honor, Face, Dignity) |>
  pivot_longer(c(Honor, Face, Dignity),
               names_to = "Dimension", values_to = "Score") |>
  mutate(Dimension = factor(Dimension, levels = c("Honor","Face","Dignity")))

# Set limits explicitly for reproducibility; alternatively use range(world_long$Score, na.rm=TRUE).
lims <- c(3,5.5) # range(world_long$Score, na.rm = TRUE)

# Centered scores: keep them separate (different palette/legend) and use symmetric limits if possible.
world_long_centered <- world_join |>
  select(geometry, HonorC, FaceC, DignityC) |>
  pivot_longer(c(HonorC, FaceC, DignityC),
               names_to = "Dimension", values_to = "Score") |>
  mutate(Dimension = factor(Dimension, levels = c("HonorC","FaceC","DignityC")))

# Prefer symmetric bounds around 0 for interpretability (edit as needed).
limsc <- c(-1,1) # range(world_long_centered$Score, na.rm = TRUE)

# --- 5) Plot: titles centered, thin white borders, compact legend ---
# Apply the same basic theme to all six maps; legends will later be collected per row.
common_theme <- theme(
  plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
  legend.position = "bottom",
  legend.title = element_text(size = 10),
  legend.text  = element_text(size = 9)
)

# Non-centered maps (viridis option "C")
p_honor <- ggplot(filter(world_long, Dimension == "Honor")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Honor norms") +
  theme_void() +
  common_theme

p_face <- ggplot(filter(world_long, Dimension == "Face")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Face norms") +
  theme_void() +
  common_theme

p_dignity <- ggplot(filter(world_long, Dimension == "Dignity")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "D",
                     limits = lims, na.value = "grey92", direction = -1) +
  labs(title = "Dignity norms") +
  theme_void() +
  common_theme

# Centered maps (viridis option "D" to visually differentiate from non-centered)
p_honorc <- ggplot(filter(world_long_centered, Dimension == "HonorC")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "C",
                     limits = limsc, na.value = "grey92", direction = -1) +
  labs(title = "Honor norms (centred)") +
  theme_void() +
  common_theme

p_facec <- ggplot(filter(world_long_centered, Dimension == "FaceC")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "C",
                     limits = limsc, na.value = "grey92", direction = -1) +
  labs(title = "Face norms (centred)") +
  theme_void() +
  common_theme

p_dignityc <- ggplot(filter(world_long_centered, Dimension == "DignityC")) +
  geom_sf(aes(fill = Score), color = "white", size = 0.1) +
  scale_fill_viridis(name = "Societal mean (1-7)", option = "C",
                     limits = limsc, na.value = "grey92", direction = -1) +
  labs(title = "Dignity norms (centred)") +
  theme_void() +
  common_theme

# ---- build two separate rows (each with its own collected legend) ----
# Keep guide collection INSIDE each row so the top row (C) and bottom row (D)
# retain different palettes and their own legends.
row_nc <- (p_honor | p_face | p_dignity) +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "right",          # put legend to the side of the row
    legend.direction = "vertical"       # vertical legend for compact height
  )

row_c <- (p_honorc | p_facec | p_dignityc) +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "right",
    legend.direction = "vertical"
  )

# Final assembly: stack the two rows. Each keeps its own legend and color scale.
final_plot <- row_nc / row_c
final_plot

# Export plot
ggsave("figures_robust/DHF_Norms_worldmap.png", final_plot,
       width = 18, height = 6, dpi = 600)
ggsave("figures_robust/DHF_Norms_worldmap.pdf", final_plot,
       width = 18, height = 6)
```

### Main study: Country-level correlates of DHF

Ecological antecedents of DHF endorsement and norms

```{r correl-table-country-level}
apaTables::apa.cor.table(
  dt4 %>% 
    select(D_normc_mean_country, H_normc_mean_country,
           F_normc_mean_country, D_endc_mean_country, 
           H_endc_mean_country, F_endc_mean_country, 
           wb_pop_density_1961, ms_pathogen_9items, 
           icb_crisis_participations, icb_avg_violence_level,
           wb_gdp_pcap_usd_1960, fiw_F_2013, 
           fiw_C_2013, fiw_Total_2013
           )
)
```
 
DHF and current country performance

```{r correl-table-country-performance}
apaTables::apa.cor.table(
  dt4 %>% 
    select(D_normc_mean_country, H_normc_mean_country,
           F_normc_mean_country, D_endc_mean_country, 
           H_endc_mean_country, F_endc_mean_country, 
           wb_gdp_pcap_usd_most_recent, gii_value_2021, 
           wb_gini_2020, fiw_Total_2023, hdi_value_2021
           )
)
```

DHF and other cultural dimensions

```{r correl-table-other-cultural}
# believe these are mean_country centered above, but should check
apaTables::apa.cor.table(
  dt4 %>% 
    select(D_normc_mean_country, H_normc_mean_country,
           F_normc_mean_country, D_endc_mean_country, 
           H_endc_mean_country, F_endc_mean_country, 
           # Openness_to_Change_mean_country,
           Openness_to_Change, 
           # Conservation_mean_country, 
           Conservation, 
           # Self_Transcendence_mean_country,
           Self_Transcendence, 
           # Self_Enhancement_mean_country, 
           Self_Enhancement, 
           tl_tightness, mk_individualism_collectivism, 
           mk_flexibility_monumentalism, rm_relational_mobility 
           # `o-c`, `st-se` 
           # not sure what these are need to update var names
           )
)
```

### Main study: Individual-level correlates of DHF

#### DHF and prosociality

[Tables in line with prereg H2-H3]

```{r h2-model}
# ============================================================================
# H2 ANALYSIS USING dt5 (PROSOCIAL OUTCOME)
# ============================================================================

# reset dt5 so that we have all the variables 
dt5 <- subset(dt4, dictator_cpass==1) 
dt5$prosocial <- as.numeric(dt5$Dictator_decision)

print("Preparing H2 analysis with misty centering")
print(paste("Dataset has", nrow(dt5), "participants"))

# Proper multilevel centering using misty package
DF_H2 <- dt5 %>% 
  mutate(
    # Group-mean centering for individual-level variables (Level 1)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full), 
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full), 
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full)
  )

# Data quality check
print("Data quality check...")
analysis_vars <- c("prosocial", "D_self_end_CWC", "D_other_end_CWC", 
                   "H_self_end_CWC", "H_other_end_CWC", 
                   "F_self_end_CWC", "F_other_end_CWC", "country_res_full")

# Check which variables exist
available_vars <- analysis_vars[analysis_vars %in% names(DF_H2)]
print("Available analysis variables:")
print(available_vars)

# Complete cases
complete_cases <- sum(complete.cases(DF_H2[, available_vars]))
print(paste("Complete cases for analysis:", complete_cases, "out of", nrow(DF_H2)))

# Country sample sizes
country_sizes <- DF_H2 %>%
  filter(!is.na(prosocial)) %>%
  group_by(country_res_full) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

print("Sample sizes by country (top 10):")
print(head(country_sizes, 10))
print(paste("Number of countries:", nrow(country_sizes)))
print(paste("Minimum country sample size:", min(country_sizes$n)))

# H2 Main Analysis - six factors model 
print("\nRunning H2 Analysis - Six DHF Facets Model...")

h2.fit <- lmer(prosocial ~ D_self_end_CWC + D_other_end_CWC + 
                 H_self_end_CWC + H_other_end_CWC + 
                 F_self_end_CWC + F_other_end_CWC +
                 (1|country_res_full), 
               data = DF_H2,
               REML = FALSE)

print("H2 MODEL RESULTS:")
h2_params <- parameters(h2.fit, standardize = "refit", ci = 0.95)
print(h2_params)

# Model performance
print("\nModel Performance:")
perf <- performance(h2.fit)
print(perf)

# R-squared values
r2_vals <- r2(h2.fit)
print(paste("Marginal R² (fixed effects):", round(r2_vals$R2_marginal, 3)))
print(paste("Conditional R² (fixed + random):", round(r2_vals$R2_conditional, 3)))

# Check column names and create standardized results table
print("\nColumn names in h2_params:")
print(names(h2_params))

# Create standardized results table with proper column references
print("\nStandardized Coefficients with 95% CI and p-values:")
h2_results <- data.frame(
  Parameter = h2_params$Parameter,
  Std_Beta = round(h2_params$Coefficient, 4),  # Using Coefficient instead of Std_Coefficient
  CI_Lower = round(h2_params$CI_low, 4),
  CI_Upper = round(h2_params$CI_high, 4),
  p_value = round(h2_params$p, 4),
  Significance = ifelse(h2_params$p < 0.001, "***",
                        ifelse(h2_params$p < 0.01, "**",
                               ifelse(h2_params$p < 0.05, "*", "")))
)
print(h2_results)

# Random effects
rand_effects <- VarCorr(h2.fit)
print("\nRandom Effects Variance:")
print(rand_effects)
```

```{r h3-model}
# ============================================================================
# H3 ANALYSIS - MULTILEVEL PATH MODELS
# ===========================================================================

# STEP 1: Prepare prosocial data (dt5) with proper misty centering
print("Preparing prosocial model data from dt5...")
DF_prosocial_H3 <- dt5 %>%
  filter(!is.na(prosocial) & !is.na(D_end) & !is.na(H_end) & !is.na(F_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: grand-mean centering (CGM)
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("Prosocial model sample size:", nrow(DF_prosocial_H3)))

# STEP 2: Prepare reciprocity data (dt6) with proper misty centering
# reset dt6 since it doesn't have these variables 
dt6 <- subset(dt4, ultimatum_cpass==1) #N=20626

# Merge with dt6
dt6 <- merge(dt6, neg_rec_df, by="ResponseId")
dt6$UG_negrec <- as.numeric(dt6$UG_negrec)
dt6 <- merge(dt6, pos_rec_df, by="ResponseId")

print("Preparing reciprocity model data from dt6...")
DF_reciprocity_H3 <- dt6 %>%
  filter(!is.na(UG_posrec) & !is.na(UG_negrec) & 
           !is.na(D_end) & !is.na(H_end) & !is.na(F_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: grand-mean centering (CGM) 
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("Reciprocity model sample size:", nrow(DF_reciprocity_H3)))

# STEP 3: H3 Model 1 - Prosocial Behavior
print("\nRunning H3 Model 1: Prosocial Behavior...")

prosocial.model <- '
# Level 1: Individual endorsement predicting prosocial behavior
prosocial ~ D_end_CWC + H_end_CWC + F_end_CWC

# Level 2: Country-level norms predicting prosocial behavior  
prosocial ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

prosocial.fit <- sem(
  model = prosocial.model,
  data = DF_prosocial_H3,
  cluster = "country_res_full"
)

print("PROSOCIAL MODEL RESULTS:")
print(summary(prosocial.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for prosocial model
prosocial_std <- standardizedSolution(prosocial.fit, ci = TRUE, level = 0.95)
prosocial_reg <- prosocial_std[prosocial_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
prosocial_results <- data.frame(
  Parameter = prosocial_reg$rhs,
  Std_Beta = round(prosocial_reg$est.std, 4),
  CI_Lower = round(prosocial_reg$ci.lower, 4), 
  CI_Upper = round(prosocial_reg$ci.upper, 4),
  p_value = round(prosocial_reg$pvalue, 4),
  Significance = ifelse(prosocial_reg$pvalue < 0.001, "***",
                        ifelse(prosocial_reg$pvalue < 0.01, "**",
                               ifelse(prosocial_reg$pvalue < 0.05, "*", "")))
)
print(prosocial_results)

# STEP 4: H3 Model 2 - Positive Reciprocity
print("\nRunning H3 Model 2: Positive Reciprocity...")

posrec.model <- '
# Level 1: Individual endorsement predicting positive reciprocity
UG_posrec ~ D_end_CWC + H_end_CWC + F_end_CWC

# Level 2: Country-level norms predicting positive reciprocity
UG_posrec ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

posrec.fit <- sem(
  model = posrec.model,
  data = DF_reciprocity_H3,
  cluster = "country_res_full"
)

print("POSITIVE RECIPROCITY MODEL RESULTS:")
print(summary(posrec.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for positive reciprocity model
posrec_std <- standardizedSolution(posrec.fit, ci = TRUE, level = 0.95)
posrec_reg <- posrec_std[posrec_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
posrec_results <- data.frame(
  Parameter = posrec_reg$rhs,
  Std_Beta = round(posrec_reg$est.std, 4),
  CI_Lower = round(posrec_reg$ci.lower, 4),
  CI_Upper = round(posrec_reg$ci.upper, 4),
  p_value = round(posrec_reg$pvalue, 4),
  Significance = ifelse(posrec_reg$pvalue < 0.001, "***",
                        ifelse(posrec_reg$pvalue < 0.01, "**",
                               ifelse(posrec_reg$pvalue < 0.05, "*", "")))
)
print(posrec_results)

# STEP 5: H3 Model 3 - Negative Reciprocity  
print("\nRunning H3 Model 3: Negative Reciprocity...")

negrec.model <- '
# Level 1: Individual endorsement predicting negative reciprocity
UG_negrec ~ D_end_CWC + H_end_CWC + F_end_CWC

# Level 2: Country-level norms predicting negative reciprocity
UG_negrec ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

negrec.fit <- sem(
  model = negrec.model,
  data = DF_reciprocity_H3,
  cluster = "country_res_full"
)

print("NEGATIVE RECIPROCITY MODEL RESULTS:")
print(summary(negrec.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for negative reciprocity model
negrec_std <- standardizedSolution(negrec.fit, ci = TRUE, level = 0.95)
negrec_reg <- negrec_std[negrec_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
negrec_results <- data.frame(
  Parameter = negrec_reg$rhs,
  Std_Beta = round(negrec_reg$est.std, 4),
  CI_Lower = round(negrec_reg$ci.lower, 4),
  CI_Upper = round(negrec_reg$ci.upper, 4),
  p_value = round(negrec_reg$pvalue, 4),
  Significance = ifelse(negrec_reg$pvalue < 0.001, "***",
                        ifelse(negrec_reg$pvalue < 0.01, "**",
                               ifelse(negrec_reg$pvalue < 0.05, "*", "")))
)
print(negrec_results)


# R-squared comparison
print("\nR-SQUARED COMPARISON:")
cat("Prosocial Behavior: R² = ", round(inspect(prosocial.fit, "r2"), 3), "\n")
cat("Positive Reciprocity: R² = ", round(inspect(posrec.fit, "r2"), 3), "\n") 
cat("Negative Reciprocity: R² = ", round(inspect(negrec.fit, "r2"), 3), "\n")


print("\nH2 MODEL - Standardized Coefficients with 95% CI:")
print(h2_results)
print("\nPROSOCIAL MODEL - Standardized Coefficients with 95% CI:")
print(prosocial_results)
print("\nPOSITIVE RECIPROCITY MODEL - Standardized Coefficients with 95% CI:")
print(posrec_results)

print("\nNEGATIVE RECIPROCITY MODEL - Standardized Coefficients with 95% CI:")
print(negrec_results)
```

```{r h3-modelm-supplementary}
# ============================================================================
# H3 ANALYSIS - MULTILEVEL PATH MODELS WITH 6-FACTOR INDIVIDUAL PREDICTORS
# ============================================================================

print("Preparing H3 multilevel path model analysis with 6-factor individual predictors...")
print("Using dt5 for prosocial, dt6 for reciprocity outcomes...")

# STEP 1: Prepare prosocial data (dt5) with 6-factor individual predictors + country norms
print("Preparing prosocial model data from dt5...")
DF_prosocial_H3_6factor <- dt5 %>%
  filter(!is.na(prosocial) & 
           !is.na(D_self_end) & !is.na(D_other_end) & 
           !is.na(H_self_end) & !is.na(H_other_end) & 
           !is.na(F_self_end) & !is.na(F_other_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: grand-mean centering (CGM)
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("Prosocial model sample size:", nrow(DF_prosocial_H3_6factor)))

# STEP 2: Prepare reciprocity data (dt6) with 6-factor individual predictors + country norms
print("Preparing reciprocity model data from dt6...")
DF_reciprocity_H3_6factor <- dt6 %>%
  filter(!is.na(UG_posrec) & !is.na(UG_negrec) & 
           !is.na(D_self_end) & !is.na(D_other_end) & 
           !is.na(H_self_end) & !is.na(H_other_end) & 
           !is.na(F_self_end) & !is.na(F_other_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: grand-mean centering (CGM) 
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("Reciprocity model sample size:", nrow(DF_reciprocity_H3_6factor)))

# STEP 3: H3 Model 1 - Prosocial Behavior (6-factor individual predictors)
print("\nRunning H3 Model 1: Prosocial Behavior with 6-Factor Individual Predictors...")

prosocial_6factor.model <- '
# Level 1: 6-factor individual endorsement predicting prosocial behavior
prosocial ~ D_self_end_CWC + D_other_end_CWC + 
            H_self_end_CWC + H_other_end_CWC + 
            F_self_end_CWC + F_other_end_CWC

# Level 2: Country-level norms predicting prosocial behavior  
prosocial ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

prosocial_6factor.fit <- sem(
  model = prosocial_6factor.model,
  data = DF_prosocial_H3_6factor,
  cluster = "country_res_full"
)

print("PROSOCIAL MODEL RESULTS (6-Factor Individual Predictors):")
print(summary(prosocial_6factor.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for prosocial model
prosocial_6factor_std <- standardizedSolution(prosocial_6factor.fit, ci = TRUE, level = 0.95)
prosocial_6factor_reg <- prosocial_6factor_std[prosocial_6factor_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
prosocial_6factor_results <- data.frame(
  Parameter = prosocial_6factor_reg$rhs,
  Std_Beta = round(prosocial_6factor_reg$est.std, 4),
  CI_Lower = round(prosocial_6factor_reg$ci.lower, 4), 
  CI_Upper = round(prosocial_6factor_reg$ci.upper, 4),
  p_value = round(prosocial_6factor_reg$pvalue, 4),
  Significance = ifelse(prosocial_6factor_reg$pvalue < 0.001, "***",
                        ifelse(prosocial_6factor_reg$pvalue < 0.01, "**",
                               ifelse(prosocial_6factor_reg$pvalue < 0.05, "*", "")))
)
print(prosocial_6factor_results)

# STEP 4: H3 Model 2 - Positive Reciprocity (6-factor individual predictors)
print("\nRunning H3 Model 2: Positive Reciprocity with 6-Factor Individual Predictors...")

posrec_6factor.model <- '
# Level 1: 6-factor individual endorsement predicting positive reciprocity
UG_posrec ~ D_self_end_CWC + D_other_end_CWC + 
            H_self_end_CWC + H_other_end_CWC + 
            F_self_end_CWC + F_other_end_CWC

# Level 2: Country-level norms predicting positive reciprocity
UG_posrec ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

posrec_6factor.fit <- sem(
  model = posrec_6factor.model,
  data = DF_reciprocity_H3_6factor,
  cluster = "country_res_full"
)

print("POSITIVE RECIPROCITY MODEL RESULTS (6-Factor Individual Predictors):")
print(summary(posrec_6factor.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for positive reciprocity model
posrec_6factor_std <- standardizedSolution(posrec_6factor.fit, ci = TRUE, level = 0.95)
posrec_6factor_reg <- posrec_6factor_std[posrec_6factor_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
posrec_6factor_results <- data.frame(
  Parameter = posrec_6factor_reg$rhs,
  Std_Beta = round(posrec_6factor_reg$est.std, 4),
  CI_Lower = round(posrec_6factor_reg$ci.lower, 4),
  CI_Upper = round(posrec_6factor_reg$ci.upper, 4),
  p_value = round(posrec_6factor_reg$pvalue, 4),
  Significance = ifelse(posrec_6factor_reg$pvalue < 0.001, "***",
                        ifelse(posrec_6factor_reg$pvalue < 0.01, "**",
                               ifelse(posrec_6factor_reg$pvalue < 0.05, "*", "")))
)
print(posrec_6factor_results)

# STEP 5: H3 Model 3 - Negative Reciprocity (6-factor individual predictors)
print("\nRunning H3 Model 3: Negative Reciprocity with 6-Factor Individual Predictors...")

negrec_6factor.model <- '
# Level 1: 6-factor individual endorsement predicting negative reciprocity
UG_negrec ~ D_self_end_CWC + D_other_end_CWC + 
            H_self_end_CWC + H_other_end_CWC + 
            F_self_end_CWC + F_other_end_CWC

# Level 2: Country-level norms predicting negative reciprocity
UG_negrec ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

negrec_6factor.fit <- sem(
  model = negrec_6factor.model,
  data = DF_reciprocity_H3_6factor,
  cluster = "country_res_full"
)

print("NEGATIVE RECIPROCITY MODEL RESULTS (6-Factor Individual Predictors):")
print(summary(negrec_6factor.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for negative reciprocity model
negrec_6factor_std <- standardizedSolution(negrec_6factor.fit, ci = TRUE, level = 0.95)
negrec_6factor_reg <- negrec_6factor_std[negrec_6factor_std$op == "~",]
print("\nStandardized Coefficients with 95% CI:")
negrec_6factor_results <- data.frame(
  Parameter = negrec_6factor_reg$rhs,
  Std_Beta = round(negrec_6factor_reg$est.std, 4),
  CI_Lower = round(negrec_6factor_reg$ci.lower, 4),
  CI_Upper = round(negrec_6factor_reg$ci.upper, 4),
  p_value = round(negrec_6factor_reg$pvalue, 4),
  Significance = ifelse(negrec_6factor_reg$pvalue < 0.001, "***",
                        ifelse(negrec_6factor_reg$pvalue < 0.01, "**",
                               ifelse(negrec_6factor_reg$pvalue < 0.05, "*", "")))
)
print(negrec_6factor_results)


# R-squared comparison
print("\nR-SQUARED COMPARISON:")
cat("Prosocial Behavior (6-factor): R² = ", round(inspect(prosocial_6factor.fit, "r2"), 3), "\n")
cat("Positive Reciprocity (6-factor): R² = ", round(inspect(posrec_6factor.fit, "r2"), 3), "\n") 
cat("Negative Reciprocity (6-factor): R² = ", round(inspect(negrec_6factor.fit, "r2"), 3), "\n")

print("\nPROSOCIAL MODEL (6-Factor) - Standardized Coefficients with 95% CI:")
print(prosocial_6factor_results)

print("\nPOSITIVE RECIPROCITY MODEL (6-Factor) - Standardized Coefficients with 95% CI:")
print(posrec_6factor_results)

print("\nNEGATIVE RECIPROCITY MODEL (6-Factor) - Standardized Coefficients with 95% CI:")
print(negrec_6factor_results)
```

```{r h3-modelm-supplementary-self-reported}
# ============================================================================
# SELF-REPORTED RECIPROCITY ANALYSIS - MULTILEVEL PATH MODELS
# Using dt4 dataset with Positive_Reciprocity and Negative_Reciprocity outcomes
# ============================================================================

# ============================================================================
# PART A: MODELS WITH NORM-BASED COUNTRY-LEVEL PREDICTORS
# ============================================================================


# STEP 1A: Prepare data with norm-based country predictors (3-factor individual)
print("Preparing data for 3-factor individual + norm-based country models...")
DF_selfreport_norms_3factor <- dt4 %>%
  filter(!is.na(Positive_Reciprocity) & !is.na(Negative_Reciprocity) &
           !is.na(D_end) & !is.na(H_end) & !is.na(F_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: 3-factor model with group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: norm-based grand-mean centering (CGM)
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("3-factor norm-based model sample size:", nrow(DF_selfreport_norms_3factor)))

# STEP 2A: Prepare data with norm-based country predictors (6-factor individual)
print("Preparing data for 6-factor individual + norm-based country models...")
DF_selfreport_norms_6factor <- dt4 %>%
  filter(!is.na(Positive_Reciprocity) & !is.na(Negative_Reciprocity) &
           !is.na(D_self_end) & !is.na(D_other_end) & 
           !is.na(H_self_end) & !is.na(H_other_end) & 
           !is.na(F_self_end) & !is.na(F_other_end) &
           !is.na(D_norm_mean_country) & !is.na(H_norm_mean_country) & !is.na(F_norm_mean_country)) %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: norm-based grand-mean centering (CGM)
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

print(paste("6-factor norm-based model sample size:", nrow(DF_selfreport_norms_6factor)))

# ============================================================================
# PART B: MODELS WITH ENDORSEMENT-BASED COUNTRY-LEVEL PREDICTORS
# ============================================================================

# STEP 1B: Prepare data with endorsement-based country predictors (3-factor individual)
print("Preparing data for 3-factor individual + endorsement-based country models...")
DF_selfreport_endorse_3factor <- dt4 %>%
  filter(!is.na(Positive_Reciprocity) & !is.na(Negative_Reciprocity) &
           !is.na(D_end) & !is.na(H_end) & !is.na(F_end) &
           !is.na(D_end_mean_country) & !is.na(H_end_mean_country) & !is.na(F_end_mean_country)) %>%
  mutate(
    # Individual-level variables: 3-factor model with group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: endorsement-based grand-mean centering (CGM)
    D_end_agg_CGM = center(D_end_mean_country, type = "CGM"),
    H_end_agg_CGM = center(H_end_mean_country, type = "CGM"),
    F_end_agg_CGM = center(F_end_mean_country, type = "CGM")
  )

print(paste("3-factor endorsement-based model sample size:", nrow(DF_selfreport_endorse_3factor)))

# STEP 2B: Prepare data with endorsement-based country predictors (6-factor individual)
print("Preparing data for 6-factor individual + endorsement-based country models...")
DF_selfreport_endorse_6factor <- dt4 %>%
  filter(!is.na(Positive_Reciprocity) & !is.na(Negative_Reciprocity) &
           !is.na(D_self_end) & !is.na(D_other_end) & 
           !is.na(H_self_end) & !is.na(H_other_end) & 
           !is.na(F_self_end) & !is.na(F_other_end) &
           !is.na(D_end_mean_country) & !is.na(H_end_mean_country) & !is.na(F_end_mean_country)) %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: endorsement-based grand-mean centering (CGM)
    D_end_agg_CGM = center(D_end_mean_country, type = "CGM"),
    H_end_agg_CGM = center(H_end_mean_country, type = "CGM"),
    F_end_agg_CGM = center(F_end_mean_country, type = "CGM")
  )

print(paste("6-factor endorsement-based model sample size:", nrow(DF_selfreport_endorse_6factor)))

# ============================================================================
# MODEL 1: POSITIVE RECIPROCITY - 3-FACTOR INDIVIDUAL + NORM-BASED COUNTRY
# ============================================================================

posrec_3factor_norms.model <- '
# Level 1: Individual endorsement predicting positive reciprocity
Positive_Reciprocity ~ D_end_CWC + H_end_CWC + F_end_CWC

# Level 2: Country-level norms predicting positive reciprocity
Positive_Reciprocity ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

posrec_3factor_norms.fit <- sem(
  model = posrec_3factor_norms.model,
  data = DF_selfreport_norms_3factor,
  cluster = "country_res_full"
)

print("POSITIVE RECIPROCITY - 3-Factor Individual + Norm-Based Country:")
print(summary(posrec_3factor_norms.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results
posrec_3factor_norms_std <- standardizedSolution(posrec_3factor_norms.fit, ci = TRUE, level = 0.95)
posrec_3factor_norms_reg <- posrec_3factor_norms_std[posrec_3factor_norms_std$op == "~",]
posrec_3factor_norms_results <- data.frame(
  Parameter = posrec_3factor_norms_reg$rhs,
  Std_Beta = round(posrec_3factor_norms_reg$est.std, 4),
  CI_Lower = round(posrec_3factor_norms_reg$ci.lower, 4),
  CI_Upper = round(posrec_3factor_norms_reg$ci.upper, 4),
  p_value = round(posrec_3factor_norms_reg$pvalue, 4),
  Significance = ifelse(posrec_3factor_norms_reg$pvalue < 0.001, "***",
                        ifelse(posrec_3factor_norms_reg$pvalue < 0.01, "**",
                               ifelse(posrec_3factor_norms_reg$pvalue < 0.05, "*", "")))
)
print(posrec_3factor_norms_results)

# ============================================================================
# MODEL 2: NEGATIVE RECIPROCITY - 3-FACTOR INDIVIDUAL + NORM-BASED COUNTRY
# ============================================================================

negrec_3factor_norms.model <- '
# Level 1: Individual endorsement predicting negative reciprocity
Negative_Reciprocity ~ D_end_CWC + H_end_CWC + F_end_CWC

# Level 2: Country-level norms predicting negative reciprocity
Negative_Reciprocity ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

negrec_3factor_norms.fit <- sem(
  model = negrec_3factor_norms.model,
  data = DF_selfreport_norms_3factor,
  cluster = "country_res_full"
)

print("NEGATIVE RECIPROCITY - 3-Factor Individual + Norm-Based Country:")
print(summary(negrec_3factor_norms.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results
negrec_3factor_norms_std <- standardizedSolution(negrec_3factor_norms.fit, ci = TRUE, level = 0.95)
negrec_3factor_norms_reg <- negrec_3factor_norms_std[negrec_3factor_norms_std$op == "~",]
negrec_3factor_norms_results <- data.frame(
  Parameter = negrec_3factor_norms_reg$rhs,
  Std_Beta = round(negrec_3factor_norms_reg$est.std, 4),
  CI_Lower = round(negrec_3factor_norms_reg$ci.lower, 4),
  CI_Upper = round(negrec_3factor_norms_reg$ci.upper, 4),
  p_value = round(negrec_3factor_norms_reg$pvalue, 4),
  Significance = ifelse(negrec_3factor_norms_reg$pvalue < 0.001, "***",
                        ifelse(negrec_3factor_norms_reg$pvalue < 0.01, "**",
                               ifelse(negrec_3factor_norms_reg$pvalue < 0.05, "*", "")))
)
print(negrec_3factor_norms_results)

# ============================================================================
# MODEL 3: POSITIVE RECIPROCITY - 6-FACTOR INDIVIDUAL + NORM-BASED COUNTRY
# ============================================================================

posrec_6factor_norms.model <- '
# Level 1: 6-factor individual endorsement predicting positive reciprocity
Positive_Reciprocity ~ D_self_end_CWC + D_other_end_CWC + 
                      H_self_end_CWC + H_other_end_CWC + 
                      F_self_end_CWC + F_other_end_CWC

# Level 2: Country-level norms predicting positive reciprocity
Positive_Reciprocity ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

posrec_6factor_norms.fit <- sem(
  model = posrec_6factor_norms.model,
  data = DF_selfreport_norms_6factor,
  cluster = "country_res_full"
)

print("POSITIVE RECIPROCITY - 6-Factor Individual + Norm-Based Country:")
print(summary(posrec_6factor_norms.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results
posrec_6factor_norms_std <- standardizedSolution(posrec_6factor_norms.fit, ci = TRUE, level = 0.95)
posrec_6factor_norms_reg <- posrec_6factor_norms_std[posrec_6factor_norms_std$op == "~",]
posrec_6factor_norms_results <- data.frame(
  Parameter = posrec_6factor_norms_reg$rhs,
  Std_Beta = round(posrec_6factor_norms_reg$est.std, 4),
  CI_Lower = round(posrec_6factor_norms_reg$ci.lower, 4),
  CI_Upper = round(posrec_6factor_norms_reg$ci.upper, 4),
  p_value = round(posrec_6factor_norms_reg$pvalue, 4),
  Significance = ifelse(posrec_6factor_norms_reg$pvalue < 0.001, "***",
                        ifelse(posrec_6factor_norms_reg$pvalue < 0.01, "**",
                               ifelse(posrec_6factor_norms_reg$pvalue < 0.05, "*", "")))
)
print(posrec_6factor_norms_results)

# ============================================================================
# MODEL 4: NEGATIVE RECIPROCITY - 6-FACTOR INDIVIDUAL + NORM-BASED COUNTRY
# ============================================================================

negrec_6factor_norms.model <- '
# Level 1: 6-factor individual endorsement predicting negative reciprocity
Negative_Reciprocity ~ D_self_end_CWC + D_other_end_CWC + 
                      H_self_end_CWC + H_other_end_CWC + 
                      F_self_end_CWC + F_other_end_CWC

# Level 2: Country-level norms predicting negative reciprocity
Negative_Reciprocity ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
'

negrec_6factor_norms.fit <- sem(
  model = negrec_6factor_norms.model,
  data = DF_selfreport_norms_6factor,
  cluster = "country_res_full"
)

print("NEGATIVE RECIPROCITY - 6-Factor Individual + Norm-Based Country:")
print(summary(negrec_6factor_norms.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results
negrec_6factor_norms_std <- standardizedSolution(negrec_6factor_norms.fit, ci = TRUE, level = 0.95)
negrec_6factor_norms_reg <- negrec_6factor_norms_std[negrec_6factor_norms_std$op == "~",]
negrec_6factor_norms_results <- data.frame(
  Parameter = negrec_6factor_norms_reg$rhs,
  Std_Beta = round(negrec_6factor_norms_reg$est.std, 4),
  CI_Lower = round(negrec_6factor_norms_reg$ci.lower, 4),
  CI_Upper = round(negrec_6factor_norms_reg$ci.upper, 4),
  p_value = round(negrec_6factor_norms_reg$pvalue, 4),
  Significance = ifelse(negrec_6factor_norms_reg$pvalue < 0.001, "***",
                        ifelse(negrec_6factor_norms_reg$pvalue < 0.01, "**",
                               ifelse(negrec_6factor_norms_reg$pvalue < 0.05, "*", "")))
)
print(negrec_6factor_norms_results)

# ============================================================================
# MODELS 5-8: ENDORSEMENT-BASED COUNTRY PREDICTORS
# ============================================================================

# MODEL 5: POSITIVE RECIPROCITY - 3-FACTOR INDIVIDUAL + ENDORSEMENT-BASED COUNTRY
print("\nMODEL 5: POSITIVE RECIPROCITY - 3-Factor Individual + Endorsement-Based Country")

posrec_3factor_endorse.model <- '
Positive_Reciprocity ~ D_end_CWC + H_end_CWC + F_end_CWC
Positive_Reciprocity ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
'

posrec_3factor_endorse.fit <- sem(
  model = posrec_3factor_endorse.model,
  data = DF_selfreport_endorse_3factor,
  cluster = "country_res_full"
)

print(summary(posrec_3factor_endorse.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for Model 5
posrec_3factor_endorse_std <- standardizedSolution(posrec_3factor_endorse.fit, ci = TRUE, level = 0.95)
posrec_3factor_endorse_reg <- posrec_3factor_endorse_std[posrec_3factor_endorse_std$op == "~",]
posrec_3factor_endorse_results <- data.frame(
  Parameter = posrec_3factor_endorse_reg$rhs,
  Std_Beta = round(posrec_3factor_endorse_reg$est.std, 4),
  CI_Lower = round(posrec_3factor_endorse_reg$ci.lower, 4),
  CI_Upper = round(posrec_3factor_endorse_reg$ci.upper, 4),
  p_value = round(posrec_3factor_endorse_reg$pvalue, 4),
  Significance = ifelse(posrec_3factor_endorse_reg$pvalue < 0.001, "***",
                        ifelse(posrec_3factor_endorse_reg$pvalue < 0.01, "**",
                               ifelse(posrec_3factor_endorse_reg$pvalue < 0.05, "*", "")))
)
print("\nStandardized Coefficients with 95% CI:")
print(posrec_3factor_endorse_results)

# MODEL 6: NEGATIVE RECIPROCITY - 3-FACTOR INDIVIDUAL + ENDORSEMENT-BASED COUNTRY
print("\nMODEL 6: NEGATIVE RECIPROCITY - 3-Factor Individual + Endorsement-Based Country")

negrec_3factor_endorse.model <- '
Negative_Reciprocity ~ D_end_CWC + H_end_CWC + F_end_CWC
Negative_Reciprocity ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
'

negrec_3factor_endorse.fit <- sem(
  model = negrec_3factor_endorse.model,
  data = DF_selfreport_endorse_3factor,
  cluster = "country_res_full"
)

print(summary(negrec_3factor_endorse.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for Model 6
negrec_3factor_endorse_std <- standardizedSolution(negrec_3factor_endorse.fit, ci = TRUE, level = 0.95)
negrec_3factor_endorse_reg <- negrec_3factor_endorse_std[negrec_3factor_endorse_std$op == "~",]
negrec_3factor_endorse_results <- data.frame(
  Parameter = negrec_3factor_endorse_reg$rhs,
  Std_Beta = round(negrec_3factor_endorse_reg$est.std, 4),
  CI_Lower = round(negrec_3factor_endorse_reg$ci.lower, 4),
  CI_Upper = round(negrec_3factor_endorse_reg$ci.upper, 4),
  p_value = round(negrec_3factor_endorse_reg$pvalue, 4),
  Significance = ifelse(negrec_3factor_endorse_reg$pvalue < 0.001, "***",
                        ifelse(negrec_3factor_endorse_reg$pvalue < 0.01, "**",
                               ifelse(negrec_3factor_endorse_reg$pvalue < 0.05, "*", "")))
)
print("\nStandardized Coefficients with 95% CI:")
print(negrec_3factor_endorse_results)

# MODEL 7: POSITIVE RECIPROCITY - 6-FACTOR INDIVIDUAL + ENDORSEMENT-BASED COUNTRY
print("\nMODEL 7: POSITIVE RECIPROCITY - 6-Factor Individual + Endorsement-Based Country")

posrec_6factor_endorse.model <- '
Positive_Reciprocity ~ D_self_end_CWC + D_other_end_CWC + 
                      H_self_end_CWC + H_other_end_CWC + 
                      F_self_end_CWC + F_other_end_CWC
Positive_Reciprocity ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
'

posrec_6factor_endorse.fit <- sem(
  model = posrec_6factor_endorse.model,
  data = DF_selfreport_endorse_6factor,
  cluster = "country_res_full"
)

print(summary(posrec_6factor_endorse.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for Model 7
posrec_6factor_endorse_std <- standardizedSolution(posrec_6factor_endorse.fit, ci = TRUE, level = 0.95)
posrec_6factor_endorse_reg <- posrec_6factor_endorse_std[posrec_6factor_endorse_std$op == "~",]
posrec_6factor_endorse_results <- data.frame(
  Parameter = posrec_6factor_endorse_reg$rhs,
  Std_Beta = round(posrec_6factor_endorse_reg$est.std, 4),
  CI_Lower = round(posrec_6factor_endorse_reg$ci.lower, 4),
  CI_Upper = round(posrec_6factor_endorse_reg$ci.upper, 4),
  p_value = round(posrec_6factor_endorse_reg$pvalue, 4),
  Significance = ifelse(posrec_6factor_endorse_reg$pvalue < 0.001, "***",
                        ifelse(posrec_6factor_endorse_reg$pvalue < 0.01, "**",
                               ifelse(posrec_6factor_endorse_reg$pvalue < 0.05, "*", "")))
)
print("\nStandardized Coefficients with 95% CI:")
print(posrec_6factor_endorse_results)

# MODEL 8: NEGATIVE RECIPROCITY - 6-FACTOR INDIVIDUAL + ENDORSEMENT-BASED COUNTRY
print("\nMODEL 8: NEGATIVE RECIPROCITY - 6-Factor Individual + Endorsement-Based Country")

negrec_6factor_endorse.model <- '
Negative_Reciprocity ~ D_self_end_CWC + D_other_end_CWC + 
                      H_self_end_CWC + H_other_end_CWC + 
                      F_self_end_CWC + F_other_end_CWC
Negative_Reciprocity ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
'

negrec_6factor_endorse.fit <- sem(
  model = negrec_6factor_endorse.model,
  data = DF_selfreport_endorse_6factor,
  cluster = "country_res_full"
)

print(summary(negrec_6factor_endorse.fit, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE))

# Extract standardized results for Model 8
negrec_6factor_endorse_std <- standardizedSolution(negrec_6factor_endorse.fit, ci = TRUE, level = 0.95)
negrec_6factor_endorse_reg <- negrec_6factor_endorse_std[negrec_6factor_endorse_std$op == "~",]
negrec_6factor_endorse_results <- data.frame(
  Parameter = negrec_6factor_endorse_reg$rhs,
  Std_Beta = round(negrec_6factor_endorse_reg$est.std, 4),
  CI_Lower = round(negrec_6factor_endorse_reg$ci.lower, 4),
  CI_Upper = round(negrec_6factor_endorse_reg$ci.upper, 4),
  p_value = round(negrec_6factor_endorse_reg$pvalue, 4),
  Significance = ifelse(negrec_6factor_endorse_reg$pvalue < 0.001, "***",
                        ifelse(negrec_6factor_endorse_reg$pvalue < 0.01, "**",
                               ifelse(negrec_6factor_endorse_reg$pvalue < 0.05, "*", "")))
)
print("\nStandardized Coefficients with 95% CI:")
print(negrec_6factor_endorse_results)

# ============================================================================
# COMPREHENSIVE RESULTS SUMMARY
# ============================================================================

# R-squared comparison for all models
print("\nR-SQUARED COMPARISON ACROSS ALL MODELS:")
cat("Positive Reciprocity - 3F Individual + Norms Country: R² = ", round(inspect(posrec_3factor_norms.fit, "r2"), 3), "\n")
cat("Negative Reciprocity - 3F Individual + Norms Country: R² = ", round(inspect(negrec_3factor_norms.fit, "r2"), 3), "\n")
cat("Positive Reciprocity - 6F Individual + Norms Country: R² = ", round(inspect(posrec_6factor_norms.fit, "r2"), 3), "\n")
cat("Negative Reciprocity - 6F Individual + Norms Country: R² = ", round(inspect(negrec_6factor_norms.fit, "r2"), 3), "\n")
cat("Positive Reciprocity - 3F Individual + Endorse Country: R² = ", round(inspect(posrec_3factor_endorse.fit, "r2"), 3), "\n")
cat("Negative Reciprocity - 3F Individual + Endorse Country: R² = ", round(inspect(negrec_3factor_endorse.fit, "r2"), 3), "\n")
cat("Positive Reciprocity - 6F Individual + Endorse Country: R² = ", round(inspect(posrec_6factor_endorse.fit, "r2"), 3), "\n")
cat("Negative Reciprocity - 6F Individual + Endorse Country: R² = ", round(inspect(negrec_6factor_endorse.fit, "r2"), 3), "\n")

print("\nKEY DETAILED RESULTS:")
print("\nPositive Reciprocity - 3F Individual + Norms Country:")
print(posrec_3factor_norms_results)

print("\nNegative Reciprocity - 3F Individual + Norms Country:")
print(negrec_3factor_norms_results)

print("\nPositive Reciprocity - 6F Individual + Norms Country:")
print(posrec_6factor_norms_results)

print("\nNegative Reciprocity - 6F Individual + Norms Country:")
print(negrec_6factor_norms_results)
print("\nSELF-REPORTED RECIPROCITY ANALYSIS COMPLETE")
```

#### Other attitudinal and behavioral manifestations of DHF

[Tables in line with prepreg H4-H5 + table with individual-level correlations of DHF endorsement with values and moral foundations]

```{r h4-analysis}
# Prepare dt4 with 3-factor and 6-factor individual predictors + country norms
DF_final_H4 <- dt4 %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Individual-level variables: 3-factor model with group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: grand-mean centering (CGM)
    D_norm_agg_CGM = center(D_norm_mean_country, type = "CGM"),
    H_norm_agg_CGM = center(H_norm_mean_country, type = "CGM"),
    F_norm_agg_CGM = center(F_norm_mean_country, type = "CGM")
  )

# Test hypothesis 4a (6-factor individual predictors)
h4.model.a.6f <- lmer(Total_Violence ~ D_self_end_CWC + D_other_end_CWC +
                     H_self_end_CWC + H_other_end_CWC +
                     F_self_end_CWC + F_other_end_CWC +
                     D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM + (1|country_res_full),
                   data = DF_final_H4,
                   na.action = "na.omit")
# Do not present numbers in scientific notation
#options(scipen = 999, digits = 4)
summary(h4.model.a.6f)

# Test hypothesis 4a (3-factor individual predictors)
h4.model.a.3f <- lmer(Total_Violence ~ D_end_CWC + H_end_CWC + F_end_CWC +
                     D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM + (1|country_res_full),
                   data = DF_final_H4,
                   na.action = "na.omit")
summary(h4.model.a.3f)

# Test hypotheses 4b-c (6-factor individual predictors)
h4.model.b.6f <- lmer(Other_Face_Concern ~ D_self_end_CWC + D_other_end_CWC +
                     H_self_end_CWC + H_other_end_CWC +
                     F_self_end_CWC + F_other_end_CWC +
                     D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM + (1|country_res_full),
                   data = DF_final_H4, 
                   na.action = "na.omit")
summary(h4.model.b.6f)

# Test hypotheses 4b-c (3-factor individual predictors)
h4.model.b.3f <- lmer(Other_Face_Concern ~ D_end_CWC + H_end_CWC + F_end_CWC +
                     D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM + (1|country_res_full),
                   data = DF_final_H4, 
                   na.action = "na.omit")
summary(h4.model.b.3f)
```

```{r h5-analysis}
# 6-factor individual predictors
provocation.model.6f <-'
Level: 1
  Retaliation ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
  Withdrawal ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
  Humor ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
Level: 2
  Retaliation  ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
  Withdrawal ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
  Humor ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM 
'

provocation.fit.6f <- sem(
  model = provocation.model.6f,
  data = DF_final_H4,
  cluster = "country_res_full"
)

summary(provocation.fit.6f, 
        standardized = TRUE,
        fit.measures = TRUE,
        rsquare = TRUE)

tidy(fitmeasures(provocation.fit.6f))
tidy(provocation.fit.6f)

# 3-factor individual predictors
provocation.model.3f <-'
Level: 1
  Retaliation ~ D_end_CWC + H_end_CWC + F_end_CWC
  Withdrawal ~ D_end_CWC + H_end_CWC + F_end_CWC
  Humor ~ D_end_CWC + H_end_CWC + F_end_CWC
Level: 2
  Retaliation  ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
  Withdrawal ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM
  Humor ~ D_norm_agg_CGM + H_norm_agg_CGM + F_norm_agg_CGM 
'

provocation.fit.3f <- sem(
  model = provocation.model.3f,
  data = DF_final_H4,
  cluster = "country_res_full"
)

summary(provocation.fit.3f, 
        standardized = TRUE,
        fit.measures = TRUE,
        rsquare = TRUE)

tidy(fitmeasures(provocation.fit.3f))
tidy(provocation.fit.3f)
```

```{r h4-h5-model-country-personal}
# Prepare dt4 with 3-factor and 6-factor individual predictors + country personal endorsement
DF_final_H4 <- dt4 %>%
  mutate(
    # Individual-level variables: 6-factor model with group-mean centering (CWC)
    D_self_end_CWC = center(D_self_end, type = "CWC", cluster = country_res_full),
    D_other_end_CWC = center(D_other_end, type = "CWC", cluster = country_res_full),
    H_self_end_CWC = center(H_self_end, type = "CWC", cluster = country_res_full),
    H_other_end_CWC = center(H_other_end, type = "CWC", cluster = country_res_full),
    F_self_end_CWC = center(F_self_end, type = "CWC", cluster = country_res_full),
    F_other_end_CWC = center(F_other_end, type = "CWC", cluster = country_res_full),
    
    # Individual-level variables: 3-factor model with group-mean centering (CWC)
    D_end_CWC = center(D_end, type = "CWC", cluster = country_res_full),
    H_end_CWC = center(H_end, type = "CWC", cluster = country_res_full),
    F_end_CWC = center(F_end, type = "CWC", cluster = country_res_full),
    
    # Country-level variables: personal endorsement grand-mean centering (CGM)
    D_end_agg_CGM = center(D_end_mean_country, type = "CGM"),
    H_end_agg_CGM = center(H_end_mean_country, type = "CGM"),
    F_end_agg_CGM = center(F_end_mean_country, type = "CGM")
  )

# Test hypothesis 4a (6-factor individual predictors)
h4.model.a.6f <- lmer(Total_Violence ~ D_self_end_CWC + D_other_end_CWC +
                        H_self_end_CWC + H_other_end_CWC +
                        F_self_end_CWC + F_other_end_CWC +
                        D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM + (1|country_res_full),
                      data = DF_final_H4,
                      na.action = "na.omit")

summary(h4.model.a.6f)

# Test hypothesis 4a (3-factor individual predictors)
h4.model.a.3f <- lmer(Total_Violence ~ D_end_CWC + H_end_CWC + F_end_CWC +
                        D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM + (1|country_res_full),
                      data = DF_final_H4,
                      na.action = "na.omit")

summary(h4.model.a.3f)

# Test hypotheses 4b-c (6-factor individual predictors)
h4.model.b.6f <- lmer(Other_Face_Concern ~ D_self_end_CWC + D_other_end_CWC +
                        H_self_end_CWC + H_other_end_CWC +
                        F_self_end_CWC + F_other_end_CWC +
                        D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM + (1|country_res_full),
                      data = DF_final_H4, 
                      na.action = "na.omit")

summary(h4.model.b.6f)

# Test hypotheses 4b-c (3-factor individual predictors)
h4.model.b.3f <- lmer(Other_Face_Concern ~ D_end_CWC + H_end_CWC + F_end_CWC +
                        D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM + (1|country_res_full),
                      data = DF_final_H4, 
                      na.action = "na.omit")

summary(h4.model.b.3f)

# 6-factor individual predictors
provocation.model.6f <-'
Level: 1
  Retaliation ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
  Withdrawal ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
  Humor ~ D_self_end_CWC + D_other_end_CWC + H_self_end_CWC + H_other_end_CWC + F_self_end_CWC + F_other_end_CWC
Level: 2
  Retaliation  ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
  Withdrawal ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
  Humor ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM 
'

provocation.fit.6f <- sem(
  model = provocation.model.6f,
  data = DF_final_H4,
  cluster = "country_res_full"
)

summary(provocation.fit.6f, 
        standardized = TRUE,
        fit.measures = TRUE,
        rsquare = TRUE)

tidy(fitmeasures(provocation.fit.6f))
tidy(provocation.fit.6f)

# 3-factor individual predictors
provocation.model.3f <-'
Level: 1
  Retaliation ~ D_end_CWC + H_end_CWC + F_end_CWC
  Withdrawal ~ D_end_CWC + H_end_CWC + F_end_CWC
  Humor ~ D_end_CWC + H_end_CWC + F_end_CWC
Level: 2
  Retaliation  ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
  Withdrawal ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM
  Humor ~ D_end_agg_CGM + H_end_agg_CGM + F_end_agg_CGM 
'

provocation.fit.3f <- sem(
  model = provocation.model.3f,
  data = DF_final_H4,
  cluster = "country_res_full"
)

summary(provocation.fit.3f, 
        standardized = TRUE,
        fit.measures = TRUE,
        rsquare = TRUE)

tidy(fitmeasures(provocation.fit.3f))
tidy(provocation.fit.3f)
```
